---
title: "How is this package used?"
vignette: >
  %\VignetteIndexEntry{Introduction to pkgdown}
  %\VignetteEngine{knitr::rmarkdown}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



### Aquire raster data

First of all, the raster maps need to be acquired and stored in a folder. The package is developed with a focus on [SwissMapRaster](https://shop.swisstopo.admin.ch/de/products/maps/national/digital/), but probably other raster maps will work as well. Currently only [CRS 2056](https://epsg.io/2056) is implemented. We might also include [CRS 21781](https://epsg.io/21781) at some point but that's probably it. 

The raster maps should be sorted in a folder per scale. Currently, the names of the folders must be as follows: "SMR25" for 1:25'000 maps, "SMR50" for 1:50'000 maps and so on. Rasters should not overlap or have gaps.


### Download package

Download and load the package. It is currently only available on github. 


```{r}

devtools::install_git("https://github.engineering.zhaw.ch/rata/swissmapraster.git",upgrade = F,quiet = T)
```


```{r, message=F, warning=F}
library(swissrastermaps4r)
library(dplyr)
```

### Scan Folder

Next, run the command `init_fdir()` pointing to the location (parent folder) of this maps. This command creates a "File Directory" in the package environment by scanning all folders recursively and analyzing the content. All files ending with "tif" are checked for extent, number of layers and resolution. All the mentioned attributes of each raster file, along with the file path and the extent as a geometry, are stoerd in the variable `fdir` of the package environment.


```{r}
init_fdir("C:/Users/rata/Geodata/01_Switzerland/01_Maps")
```


`init_fdir` stored an `sf` object in the package's own environment (called `packageEnv`). It's a list of all raster files, stored with their extent, scale, resolution and other information (see `init_fdir()`).


```{r}
ls(envir = packageEnv)
```


### Show available raster extents

In order to view the available extents, call the function `show_extents()`. The default method is `ggplot2`.

```{r}

library(ggplot2)
show_extents()

```


Use `method = "tmap"` to show the extents in combination with other spatial data. For example, the [boundary of switzerland](https://opendata.swiss/en/dataset/swissboundaries3d-landesgrenzen) is included in the package. Load this dataset with `data("landesgebiet")`

```{r}

data("landesgebiet")


library(tmap)

tm_shape(landesgebiet) + 
   tm_polygons() + show_extents("tmap")
```



### Retrieve single raster

Now let's look at an example where this package actually comes to some use. Say you want to plot a map of the largest cities in Switzerland. There is a sample dataset included in the package with name, location and size of the 10 largest cities in Switzerland. 

```{r}
data("gemeinden_top_centroid")


gemeinden_top_centroid
```


We can plot a simple map using the sample data already demonstrated: 

```{r}
tm_shape(landesgebiet) + 
  tm_polygons() + 
  tm_shape(gemeinden_top_centroid) + 
  tm_dots(size = "EINWOHNERZ")
```

Now if you would want to include a swiss raster map into this plot you would:

1. first decide on a scale
2. look for the relevant map numbers based on the [division ("Blatteinteilung")](https://map.geo.admin.ch/?selectedNode=node_ch.swisstopo.pixelkarte-pk50.metadata1&Y=660000&X=190000&zoom=1&bgLayer=ch.swisstopo.pixelkarte-farbe&layers=ch.swisstopo.pixelkarte-pk50.metadata&time_current=latest&lang=de&topic=ech)
3. find the appropriate raster maps based on the map numbers from the previous step
4. check raste resolutions and possilby resample all rasters to same resolution
5. merge all the relevant raster maps into a single file
6. possilbly reassign `CRS` and `colormap` 
7. import raster into `R`

This package aims to automate steps 2 - 7 with the function `get_raster()`. The function takes an `sf` object as an input. In addition, scale level (a scale 1:1'000'000 is defined as `scale = 1000`) and method with which the extent is defined (`method = `) need to be specified. Currently, two methods are implemented: `bbox` takes a bounding box while `centroid` calculates the centroid of the sf object. Both methods accept `x_add`/`y_add` with which the extent window is enlarged. Method `centroid` _requires_ `x_add`/`y_add`, since the extent windows would have x/y demensions of Zero.

```{r}

rastermap <- get_raster(features = landesgebiet,
                        scale_level = 1000,
                        method = "bbox", 
                        name = "relief")

tm_shape(rastermap) + 
  tm_rgb() + 
  tm_shape(gemeinden_top_centroid) + 
  tm_dots(size = "EINWOHNERZ")
```

### Retrieve multiple rasters

In the previouse example, little was gained using the `get_raster` function. The function get's much more useful when multiple raster are needed. Using the same dataset, we can get a raster _per city_ using the option `per_feature = T`.
```{r}

rastermap <- get_raster(features = gemeinden_top_centroid,
                        x_add = 1000,
                        y_add = 1000,
                        per_feature = T,
                        scale_level = 25,
                        method = "centroid",
                        limit = 4)

```

If multiple rasters are returned, the output is a `list()` of rasters with a length corresponding to the number of featuers (i.e. rows) in the input features. To access the first map in the list, we use the double parenthese `[[]]`.


```{r}
credits <- "Geodata \u00A9 Swisstopo"

tm_shape(rastermap[[1]]) + 
  tm_rgb() + 
  tm_credits(credits,bg.color = "white",bg.alpha = 0.8)

```


We can of course now add all of our vector data stored in the input feature. To keep things simple, we'll refrain from doing this in this example. Just one last thing: Having the maps in lists lets us wield the power of `purrr`. (`map()` is wrapped in `invisible()` to suppress item index)

```{r,results='asis'}
library(purrr)

invisible(
  map(rastermap,function(x){
  tm_shape(x) + 
    tm_rgb() +
    tm_credits(credits,bg.color = "white",bg.alpha = 0.8)
})
)
```





