---
title: "How is this package used?"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


### Acquire raster data

In a first step, the raster maps need to be acquired and stored in a folder. Unfortunately, most of the swisstopo raster maps are behind a paywall if you aren't part of [geodata4edu](https://geodata4edu.ch/).  Two scales are available publicly for free (see [#1](https://github.com/swissgeodata4r/swissrastermaps4r/issues/1)):

- [1:500'000](https://shop.swisstopo.admin.ch/en/products/maps/national/digital/srm500)
- [1:100'000](https://shop.swisstopo.admin.ch/en/products/maps/national/digital/srm1000)


The package is developed with a strong focus on the  [swisstopo](https://shop.swisstopo.admin.ch/de/products/maps/national/digital/) raster maps and hasn't been tested with other data. Therefore, only [CRS 2056](https://epsg.io/2056) and [CRS 21781](https://epsg.io/21781) are implemented.


### Data structure

Create one folder for each maptype, scale and projection. Each folder is then named `MAPTYPE_SCALE_PROJECTION` (e.g. `PK_25_2056`). Check the function `fdir_init()` to get more details on the requirements for naming the folders.

Some metadata must be derived from the filename. In order to achieve this, create a text file in each folder and change the file name of that textfile to match the naming pattern on the files within the folder. For example, the 1:500'000 raster map has the filename: 'PK500_LV95_KGRS_500_2016_1.tif'. The file structure and the corresponding ".pattern"-File should therefore look as follows:

```
Geodata/
├── PK_500_2056/
│   ├── PK500_LV95_KGRS_500_2016_1.tif
│   ├── AABBB_CCCC_DDDD_EEE_FFFF_G.pattern
```
Call `get_srm4r("search_pattern_dict")` to see the associated naming schema (i.e. the place-holders and their meanings). The function `metainfo_from_filename` is called on the file names.

**Note:**

- The character length of the naming pattern *must* match the length of the filename. In this way, different naming patterns can exist within a single folder.
- The naming pattern currently can't handle variable lengths

### Download package

Download and load the package. It is currently only available on github. 

```{r,include=F}
if("swissmapraster4r" %in% rownames(installed.packages())){
  remove.packages("swissrastermaps4r")
}

devtools::install_github("swissgeodata4r/swissrastermaps4r",upgrade = F)
```

```{r, message=F, warning=F}

# install.packages("devtools")
# devtools::install_github("swissgeodata4r/swissrastermaps4r",upgrade = F)


library(swissrastermaps4r)

```

### Scan Folder

Next, run the command `fdir_init()` pointing to the location (parent folder) of these maps. This command creates a "File Directory" in the package environment by scanning all folders recursively and analysing the content. All files ending with "tif" are checked for extent, number of layers and resolution. All the mentioned attributes of each raster file, along with the file path and the extent as a geometry, are stored in the variable `fdir` of the package environment.

```{r, eval=F,include=F}
# fdir_init("C:/Users/rata/Geodata/01_Switzerland/01_Maps")
# fdir_export("C:/Users/rata/Geodata/01_Switzerland/01_Maps/fdir.Rda")
```

```{r, eval = F}
fdir_init("C:/Users/rata/Geodata/01_Switzerland/01_Maps")
```

```{r, include=F}
fdir_import("C:/Users/rata/Geodata/01_Switzerland/01_Maps/fdir.Rda")
```

`fdir_init()` stored an `sf` object in the package's own environment (called `packageEnv`). It's a list of all raster files, stored with their extent, scale, resolution and other information (see `fdir_init()`).


```{r}
ls(envir = swissrastermapEnv)
```


### Retrieve raster (example 1)

Now let's look at an example where this package actually comes to some use. Say you want to plot a map of the largest cities in Switzerland. There is a sample dataset included in the package with name, location and size of the 10 largest cities in Switzerland. 

```{r}
data("sample_points")
data("switzerland")


sample_points
```


We can plot a simple map using the sample data already demonstrated: 

```{r}
library(tmap)

tm_shape(switzerland) + 
  tm_polygons() + 
  tm_shape(sample_points) + 
  tm_dots(size = "EINWOHNERZ") +
    tm_credits(credits("swisstopo"),bg.color = "grey",bg.alpha = 0.8)

```

Now if you would want to include a swiss raster map into this plot you would:

1. first decide on a scale
2. look for the relevant map numbers based on the [division ("Blatteinteilung")](https://map.geo.admin.ch/?selectedNode=node_ch.swisstopo.pixelkarte-pk50.metadata1&Y=660000&X=190000&zoom=1&bgLayer=ch.swisstopo.pixelkarte-farbe&layers=ch.swisstopo.pixelkarte-pk50.metadata&time_current=latest&lang=de&topic=ech)
3. find the appropriate raster map _files_ based on the map numbers from the previous step
4. import raster into `R`
5. check raster resolutions and possibly resample all rasters to same resolution
6. merge all the relevant raster maps into a single file
7. possibly reassign `CRS` and `colormap` 

This package automates steps 2 - 7 with the function `get_raster()`. The function takes an `sf` object as an input. In addition, scale level (a scale 1:1'000'000 is defined as `scale = 1000`).


```{r}

rastermap <- get_raster(switzerland)

tm_shape(rastermap) + 
  tm_rgb() + 
  tm_shape(sample_points) + 
  tm_dots(size = "EINWOHNERZ")
```

### Retrieve raster (example 2)

In the previous example, the function `get_raster()` basically called the whole raster file of the [1:100'000](https://shop.swisstopo.admin.ch/en/products/maps/national/digital/srm1000) raster map. The function is not particularly useful for such a use case. It becomes very useful however, when we want a custom extent possibly spanning over multiple rasters. This case is illustrated in the next example:
```{r}
rastermap <- get_raster(sample_points[1,],x_add = 1000,y_add = 1000)

tm_shape(rastermap) + 
  tm_raster() + 
  tm_credits(credits("swisstopo"),bg.color = "white",bg.alpha = 0.8)
```



