---
title: "Untitled"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Show available raster extents

In order to view the available extents, call the function `show_extents()`. The default method is `ggplot2`.

```{r}

library(ggplot2)
show_extents()

```


Use `method = "tmap"` to show the extents in combination with other spatial data. For example, the [boundary of switzerland](https://opendata.swiss/en/dataset/swissboundaries3d-landesgrenzen) is included in the package. Load this dataset with `data("landesgebiet")`

```{r}

data("landesgebiet")


library(tmap)

tm_shape(landesgebiet) + 
   tm_polygons() + 
  show_extents("tmap")
```



and method with which the extent is defined (`method = `) need to be specified. Currently, two methods are implemented: `bbox` takes a bounding box while `centroid` calculates the centroid of the sf object. Both methods accept `x_add`/`y_add` with which the extent window is enlarged. Method `centroid` _requires_ `x_add`/`y_add`, since the extent windows would have x/y demensions of Zero.
